A fully labelled proof system for intuitionistic modal logics

### 2020-09-22 FullyLabelled/JLC/main.tex
abstract

 \begin{abstract}
   In this paper we present a labelled sequent system for
   intuitionistic modal logics such that there is not only one, but
   two relation symbols appearing in sequents: one for the accessibility
   relation associated with the Kripke semantics for normal modal logics and
   one for the preorder relation associated with the Kripke semantics
   for intuitionistic logic.
   %%
   This puts our system in close correspondence with the standard
   birelational Kripke semantics for intuitionistic modal logics. As a
   consequence it can encompass a wider range of intuitionistic modal
   logics than existing labelled systems.
   %%
   We also show an internal cut elimination proof for our system.
 \end{abstract}

>>>>

 \begin{abstract}
   \review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
   \lutz{Done?}
   In this paper we present a labelled sequent system for
   intuitionistic modal logics such that there is not only one, but
   two relation symbols appearing in sequents: one for the accessibility
   relation associated with the Kripke semantics for normal modal logics and
   one for the preorder relation associated with the Kripke semantics
   for intuitionistic logic.
   %%
   This puts our system in close correspondence with the standard
   birelational Kripke semantics for intuitionistic modal logics. As a
   consequence it can encompass a wider range of intuitionistic modal
   logics than existing labelled systems.
   %%
   We show soundness and completeness of our system, together with an internal cut elimination proof.
   %%
   Finally, we show how the system can be extended with arbitrary intuitionistic Scott-Lemmon axioms.
 \end{abstract}
